Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-09 Manuscript/manuscript.tex
average number of contacts normalized per lipid and reported in a slightly better way in stoichiometry section of MS.

In addition, we estimated relative binding affinities 
of several moieties in POPC towards \ce{Ca^{2+}}. 
The dominant contribution
to the binding of \ce{Ca^{2+}} to POPC membranes comes from the phosphate group. 
Such a finding is supported by the calculated
number of contacts between \ce{Ca^{2+}} and POPC oxygen atoms.
The average number of contacts between \ce{Ca^{2+}} and any oxygen atom in POPC is 59.8, 
whereas if only phosphate oxygen atoms are considered 
the average number of contacts decreases only by a tiny amount to 57.2. 
We corroborate this finding with the probability isodensity contours in Fig.~\ref{fig:volmaps}, 
which are easier to interpret.

>>>>

In addition, we estimated relative binding affinities 
of several moieties in POPC towards \ce{Ca^{2+}}. 
The dominant contribution
to the binding of \ce{Ca^{2+}} to POPC membranes comes from the phosphate group. 
Such a finding is based on the calculated
number of contacts per lipid between \ce{Ca^{2+}} and POPC oxygen atoms, 
$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O}$,
in which a contact between the two groups is counted 
if their distance is less than or equal $0.3 \, \mathrm{nm}$ (robustness of this definition discussed in reference~\citenum{melcrova16}). 
The average number of contacts between \ce{Ca^{2+}} and any oxygen atom in POPC is 
$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O} = 0.47 $,    % = 59.8/128 
whereas if only phosphate oxygen atoms are considered 
the average number of contacts decreases only by a tiny amount to 
$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{PO_4} = 0.45 $,    % = 57.2/128 . 
and if only carbony oxygen atoms are considered,
this value is merely
$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} = 0.02 $.    % = (59.8-57.2)/128 . 
We corroborate this finding with the probability isodensity contours in Fig.~\ref{fig:volmaps}, 
which are easier to interpret.
